Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-09-30 main.tex
additional work ...

We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary. 
% This is inspired by the classical proof of what is often called Friedrichs' inequality.

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
\end{proof}

These constants are generally not optimal. 
For example, when $p=2$ and only the divergence is considered, 
we have the following improved estimate.

\begin{lemma}\label{lemma:PFfordivergence}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
    \begin{align*}
        \| \bfw \|_{L^{2}(\Omega)} 
        \leq 
        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This is a reduction to Friedrichs' inequality. 
    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to Friedrichs inequality. 
    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
    which has the same smallest singular value. 
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq l$
    and  
    \begin{align*}
        \cartan u = \cartan w,
        \quad 
        \| w \| 
        \leq 
        C_{\PF,\Gamma,l,k,p}(T)
        \diam(T)^{k} 
        \| \cartan u \|
        .
    \end{align*}
    Here, $C_{\PF,\Gamma,l,k,p}(T) > 0$ is a constant such that 
    \begin{align*}
        C_{\PF,\Gamma,l,k,p}(T)
        \leq 
        2^{\frac n p}
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (l+1)/n! } 
        \algebraicshapemeasure(T)^{k-1}
        \Ceins{n}(T)
        % \matnorm{\Jacobian \varphi}^{k}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
    We see that $\vol(\tilde U) = (l+1)/n!$

@@

    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
    \begin{align*}
        \| w \|_{L^{p}(T_{m+1})}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\hat T)}
        \\&
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        &\leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    The second inequality follows.
\end{proof}

@@

The main result of this manuscript is the following theorem.

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_m$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
    and such that for each $T_{m} \in \calT$ in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         C_{\PF,\Gamma,k,p}(\calT) 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k+1} 
%         \diam(T)^{k} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{\PF,\Gamma,k,p}(\calT) 
%         \diam(T)^{k} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k} 
%         \| w \|_{L^{p}(U_{m-1})}
%         \\
        &
        \leq  
        C_{\PF,\Gamma,k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(U_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    \mwl{The notation $U_m$ should be settled in the definition of shellings.}
\end{theorem}

@@

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_{m})}
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
    we can assume 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Proposition~\ref{proposition:pullbackestimate} to find 
    \begin{align*}
        \| w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \matnorm{ \Jacobian \Xi_{m} }^{k}
        \cdot 
        \| w_{m-1} \|_{L^{p}(U_{m-1})}
        ,
        \\
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \matnorm{ \Jacobian \Xi_{m} }^{k+1}
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
    We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
%     \begin{align*}
%         ...
%     \end{align*}
%     This enables the recursion
%     \begin{align*}
%         \| w_{m} \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \matnorm{ \Jacobian \Xi_{m} }^{k} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\Gamma_{m},k,p} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\Gamma_{m},k,p} 
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \matnorm{ \Jacobian \Xi_{m} }^{k+1} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         .
%     \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}

@@

    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
    By assumption, 
    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
    \begin{align*}
        \| w_{m-1} \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=0}^{m} 
        C_{???}
        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Because pullback and exterior derivative commute, 
    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
    Moreover, the desired estimate follow from Proposition~\ref{proposition:starreflection}.
    The proof is complete. 
\end{proof}

>>>>

We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary. 
% This is inspired by the classical proof of what is often called the Friedrichs inequality.

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        C_{{\rm{PF}},k,\Omega,p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    where 
    \begin{align*}
        C_{{\rm{PF}},k,\Omega,p} 
        = 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
    This follows from Theorem~\ref{theorem:PF_EC} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{n}(B_1(0)) \diam(\Omega)^{n}$.
\end{proof}

These constants are generally not optimal. 
For example, when $p=2$ and when only the divergence is considered, 
we have the following improved estimate.

\begin{lemma}\label{lemma:PFfordivergence}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set. 
    Then for each $\bfu \in \bfH(\divergence,\Omega)$ there exists $\bfw \in \bfH(\divergence,\Omega)$ with $\divergence \bfu = \divergence \bfw$ and 
    \begin{align*}
        \| \bfw \|_{L^{2}(\Omega)} 
        \leq 
        \diam(\Omega) \| \divergence \bfu \|_{L^{2}(\Omega)}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This is a reduction to the Friedrichs inequality. 
    Let $W^{1,2}_{0}(\Omega)$ be the closure of the smooth functions with support in $\Omega$ in the Hilbert space $W^{1,2}(\Omega)$. 
    Then $\nabla : W^{1,2}_{0}(\Omega) \subseteq L^{2}(\Omega) \rightarrow \bfL^{2}(\Omega)$ is a closed densely-defined linear operator 
    with smallest singular value bounded from below by $\diam(\Omega)^{-1}$, according to the Friedrichs inequality. 
    The adjoint is the closed densely-defined linear operator $\bfW^{2}(\divergence,\Omega) \subseteq \bfL^{2}(\Omega) \rightarrow L^{2}(\Omega)$,
    which has the same smallest singular value. 
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{\ell}$ be $\ell+1$ different faces of $T$. 
    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq \ell$.
    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq \ell$
    and  
    \begin{align*}
        \cartan w = \cartan u,
        \quad 
        \| w \|_{L^{p}(\Omega)} 
        \leq 
        C_{\PF,\Gamma,\ell,k,p}(T)
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Here, $C_{\PF,\Gamma,\ell,k,p}(T) > 0$ is a constant such that 
    \begin{align*}
        C_{\PF,\Gamma,\ell,k,p}(T)
        \leq 
        2^{\frac n p}
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{ (\ell+1)/n! } 
        \algebraicshapemeasure(T)^{k-1}
        \Ceins{n}(T)^{k}
        \diam(T)^{k} 
        % \matnorm{\Jacobian \varphi}^{k}
        .
    \end{align*}
\end{lemma}
\todo{MV: There is indeed $\diam(T)^{k}$, with the power $k$? Nothing like this appears in Lemma~\ref{lemma:PFexteriorsimplex}. Moreover, so far, all the constants $C_{{\rm{PF}},T,p}$, $C_{{\rm{PF}},T_1 \cup T_2,p}$ in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, $C_{\PF,T,F,p}$ in Lemma~\ref{lemma:mixedbconsimplex}, or $C_{{\rm{PF}},k,\Omega,p}$ in Lemma~\ref{lemma:PFexteriorsimplex} had the diameter $\diam(T)$ inside, only the constants in Section~\ref{section: PX_convex} have it outside. Finally, $\Omega$ in the indices is missing, whereas $l$ is superfluous. We should unify.}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$. 
    We see that $\vol(\tilde U) = (l+1)/n!$

@@

    In addition to that, by Proposition~\ref{proposition:pullbackestimate}:
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\hat T)}
        \\&
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        &\leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    \todo{MV: the norms of the Jacobians have to be fixed.}
    The second inequality follows.
    \todo{MV: Please a few more details.}
\end{proof}

@@

Suppose that an $n$-dimensional triangulation $\calT$ has a shelling $T_{0}, T_{1}, \dots, T_{M}$. 
For each $1 \leq m \leq M$, there exists a simplex $S_{m\cye{-1}} \in \calT$ 
such that $T_{m}$ is the last $n$-simplex in the shelling that belongs to $\cye{\cancel{T_{m} \in}} \patch_{\calT}(S_{m\cye{-1}})$. \cye{This is precisely $S_m \in \calT$ from Lemma~\ref{lemma:existenceofstar} (there the last simplex is called $T_{m+1}$)}.

\todo[inline]{MV: It might be good to synchronize the indices between the shellability definitions in Section~\ref{section:shellability} and Theorems~\ref{theorem:poincarefriedrichsestimate:grad}, \ref{theorem:poincarefriedrichsestimate:gradzwei}, \ref{theorem:poincarefriedrichsestimate:exterior}, \ref{theorem:poincarefriedrichsestimate:exterior:contraction}.}

We then let $U_{m \cye{-1}}$ be the closure \cye{of} $\patch_{\calT}(S_{m\cye{-1}}) \setminus T_{m}$,
and we call it the complement of $T_{m}$ in the star $\patch_{\calT}(S_{m\cye{-1}})$.

The main result of this manuscript for shellable triangulations of domains, not necessarily convex or even star-shaped, is the following theorem.

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_m$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
    and such that for each $T_{m} \in \calT$ in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         C_{\PF,\Gamma,k,p}(\calT) 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k+1} 
%         \diam(T)^{k} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{\PF,\Gamma,k,p}(\calT) 
%         \diam(T)^{k} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k} 
%         \| w \|_{L^{p}(U_{m-1})}
%         \\
        &
        \leq  
        C_{\PF,\Gamma,k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(U_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    \mwl{The notation $U_m$ should be settled in the definition of shellings.}
\end{theorem}
\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with \cye{an $n$-dimensional} shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_{\cye{M}}$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    and such that for each $T_{m} \in \calT$ in the shelling\cye{, $1 \leq m \leq M$,} 
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        C_{\PF,\cye{T_m, I_{m-1}},k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(U_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    \todo{MWL: The notation $U_m$ should be settled in the definition of shellings.}
\end{theorem}\todo{MV: I think we should also write down the bound for $\| w \|_{L^{p}(\Omega)}.$}

@@

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_{m})}
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
    we can assume 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{\PF,T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Proposition~\ref{proposition:pullbackestimate} to find 
    \begin{align*}
        \| w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \matnorm{ \Jacobian \Xi_{m} }^{k}
        \cdot 
        \| w_{m-1} \|_{L^{p}(U_{m-1})}
        ,
        \\
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \matnorm{ \Jacobian \Xi_{m} }^{k+1}
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    We have assumed that $\cartan w_{m-1} = \cartan u_{|\Omega_{m-1}}$. 
    We use the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}. 
%     \begin{align*}
%         ...
%     \end{align*}
%     This enables the recursion
%     \begin{align*}
%         \| w_{m} \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \matnorm{ \Jacobian \Xi_{m} }^{k} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\Gamma_{m},k,p} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\Gamma_{m},k,p} 
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \matnorm{ \Jacobian \Xi_{m} }^{k+1} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         .
%     \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}
\begin{proof}
    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
    By assumption, there exists a shelling $T_0, T_1, \dots, T_{\cye{M}}$. 
    We write $\Omega_m := \cup_{j=0}^{m} T_j$, \cye{$0 \leq m \leq M$,} which is \cye{by Lemma~\ref{lemma:shell_triang_man}} a triangulated $n$-dimensional submanifold with boundary. \todo[inline]{MV: It might also be good to synchronize the notations $X_{m}$ and $\Omega_m$. I would go for $X_{m}$, since this is a union of $n$-simplices (closed), whereas $\Omega_m$ has a connotation of a domain (open).}
    For $0 < m \leq M$, by \cye{the definition of shellability in Section~\ref{section:shellability}}, $T_{m}$ and $\cye{\Omega_{m-1}}$ share the interface $\cye{I}_{m\cye{-1}}$, which is a collection of faces of $T_{m}$. 
    \cye{It follows from} Lemma~\ref{lemma:existenceofstar} \cye{that} adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m\cye{-1}} \in \calT$, \cye{where} $U_{m-1} \subseteq \Omega_{m-1}$ is the complement of $T_{m}$ in that newly completed star.\todo{MV: Short, as already explained above in details.}

    \cye{We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound.} Let $u \in W^{p}\Alt^{k}(\Omega)$. 
    First, \cye{on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex},} there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
    \end{gather*}
    \cye{We define $w|_{T_0} := w_0$.}
    Suppose now that $0 < m \leq M$ such that $w\cye{|_{\Omega_{m-1}}} \in W^{p}\Alt^{k}(\Omega_{m-1})$ with $\cartan w = \cartan u$ over $\Omega_{m-1}$. \cye{This is true for $m=1$. We now define, as in~\cite[equations~(5.12) and~(5.14)]{ern2020stable} or~\cite[equations~(6.7) and~(6.9)]{Chaum_Voh_p_rob_3D_H_curl_24},
    \begin{align} \label{equation:w''_ext_der}
    w|_{T_m} := u|_{T_m} + \Xi_{m}^{\ast}((w - u)|_{U_{m-1}}),
    \end{align}
\todo[inline]{MV: Direct and simple definition. Only one object. Namely avoids the checking of the compatibility of the boundary condition, which is a bit tedious and requires a rigorous apparatus.}
    where $\Xi_{m} : T_{m} \rightarrow U_{m-1}$ is the reflection mapping
    as \cye{$\Xi_{1}$} in \cye{Proposition}~\ref{proposition:starreflection} \cye{and the pullback is defined in~\eqref{equation:pullback}}. Clearly, $w|_{T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
    \begin{align*}
        \trace_{\cye{I}_{m\cye{-1}}} w|_{T_m} = \trace_{\cye{I}_{m\cye{-1}}} w|_{\Omega_{m-1}},
    \end{align*}
    since $u$ is trace continuous over $I_{m-1}$ and $\Xi_{m}$ is the identity along $I_{m-1}$, and
    \begin{align*}
        \cartan w = \cartan u \text{ over } T_m,
    \end{align*}
    since $\cartan w = \cartan u$ over $\Omega_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
    \begin{align*}
    w|_{\Omega_{m}} \in W^{p}\Alt^{k}(\Omega_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } \Omega_{m}. 
    \end{align*}
    }

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| \cye{w} \|_{L^{p}(T_{m})}
        \leq  
        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
        + 
        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, \cye{since $\trace_{I_{m-1}} (u|_{T_m} - \Xi_{m}^{\ast}(u|_{U_{m-1}})) = 0$, we have}
    \begin{align*}
        \| \cye{u - \Xi_{m}^{\ast}(u|_{U_{m-1}})} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
        + \| \cartan (\Xi_{m}^{\ast}(u|_{U_{m-1}})) \|_{L^{p}(T_{m})} )
        .
    \end{align*}\todo{MV: $\diam(T)^{\cye{k}}$???}
    We also use \cye{Proposition}~\ref{proposition:pullbackestimate} to find 
    \begin{align*}
        \| \cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \| \Jacobian \Xi_{m} \|^{k}
        \| \cye{w} \|_{L^{p}(U_{m-1})}
        ,
        \\
        \| \cartan (\cye{\Xi_{m}^{\ast}(w|_{U_{m-1}})}) \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
        \| \Jacobian \Xi_{m} \|^{k+1}
        \| \cartan \cye{u} \|_{L^{p}(U_{m-1})}
        ,
    \end{align*}\todo{MV: Which norms of the Jacobians and their determinants?}
    \cye{where we have employed} that $\cartan w = \cartan u$ \cye{over $\Omega_{m-1}$}. 
    Using the properties of the reflection mapping in \cye{Proposition}~\ref{proposition:starreflection}, the desired recursive estimate follows. 
%     \begin{align*}
%         ...
%     \end{align*}
%     This enables the recursion
%     \begin{align*}
%         \| w_{m} \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \| \Jacobian \Xi_{m} \|^{k} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         C_{\PF,T_{m},\cye{I}_{m\cye{-1}},k,p} 
%         |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p} 
%         \| \Jacobian \Xi_{m} \|^{k+1} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         .
%     \end{align*}
\end{proof}

@@

    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Proposition~\ref{proposition:starreflection},
    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
    By assumption, 
    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
    \begin{align*}
        \| w_{m-1} \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=0}^{m} 
        C_{???}
        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Because pullback and exterior derivative commute, 
    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
    Moreover, the desired estimate follow from Proposition~\ref{proposition:starreflection}.
    The proof is complete. 
\end{proof}
\todo[inline]{MV: Why a second theorem? Difference of Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} wrt Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}? Which is better and when?}
